Multi-product Batch Processing Time Maximization Problem

### 2023-09-11 manuscript/manuscript.tex
multi-product balancing problem definition

The term multi-product batch production is usually applied to designate an intermittent production system in which batches of different products and sizes are processed one at a time, sharing the same production facilities. A multi-product batch plant basically consists of one or more units, grouped into one or more stages, and intermediate storage locations. At each stage some distinct operations are performed and the batches are processed sequentially over the stages. However, the plant layout can take on different formats, such as: single unit; serial flowshop plant, in which all products follow a linear flow through the production stages; parallel plants in which production units of the same type are arranged in parallel, forming each production stage \citep{MendezEtAll2000, ShiEtAll2017}; and networked processes, in which production units are not arranged in lines, and the connection between the units may or may not exist so that the production paths in the flowshop network can be different for each product and the passing of previous batch can be possible so that the final sequence of the production at the last stage units can be different from the initial sequence \citep{KimEtAl1996}.

The scientific literature address many different problems related to such industrial enviroment, including the design, sizing and scheduling problems. The multi-product batch plant design problem is concerned to obtain the configuration of the plant and the equipment that minimize the capital cost of all the equipment items needed to fulfill the production requirements (Ravemark and Rippin, 1998). The configuration of the plant basically consists of defining how many stages, how many units at each stage, and what capacity for intermediate storages will be necessary, as well as the best factory layout.

@@

We also have the multi-product batch scheduling (MPBS) problems, in which it is necessary to determine the ideal batch size for each product and also the production sequence of the products batches based on the known demand \citep{Eilon1985}. Here, the solution must be determined in such a way that both setup and storage costs are minimized \citep{Eilon1985, Omega1993, LiuEtAl2020}. Some cientific works impose additional constraints on the MPBS problem - such as release times and due dates for each products batch production, and sequencing constraints due to mismatched product colors sequences - and focus on other goals - such as optimize customer satisfaction and/or the plant performance \citep{MendezEtAll2000, ShiEtAll2017}. Also, the cientific works consider MPBS problems within different layouts. In parallel MPBS as well as in networked processes, it can also be necessary to define in which units each batch will be processed, and constraints that limit the units that can process each batch can also be imposed.

@@

In all papers presented above, each batch contains only one product type, and each machine can process only one batch (or product type) at a time. \cite{LiEtAl2022} deal with a PMPBS problem involving incompatible families with different job sizes and capacity constraints. In this problem, solutions are accepted in which two or more batches are processed simultaneously on the same machine. However, there are no production limitations for the production of each product group. The paper of \cite{LiEtAl2022} also presente an extensive literature review on production batch scheduling problems. Other important works deal with the problem of a multi-product batch plant design (MPBPD). In this case the problem is to obtain the configuration of the plant and the equipment that minimize the capital cost of all the equipment items needed to fulfill the production requirements (Ravemark and Rippin, 1998).

@@

>>>>

The term multi-product batch production is usually applied to designate an intermittent production system in which batches of different products and sizes are processed one at a time, sharing the same production facilities. A multi-product batch plant basically consists of one or more units, grouped into one or more stages, and possibly, intermediate storage locations. At each stage some distinct operations are performed and the batches are processed sequentially over the stages. However, the plant layout can take on different formats, such as: single unit; serial flowshop plant, in which all products follow a linear flow through the production stages; parallel plants in which production units of the same type are arranged in parallel, forming each production stage \citep{MendezEtAll2000, ShiEtAll2017}; and networked processes, in which production units are not arranged in lines, and the connection between the units may or may not exist so that the production paths in the flowshop network can be different for each product and the passing of previous batch can be possible so that the final sequence of the production at the last stage units can be different from the initial sequence \citep{KimEtAl1996}.

The scientific literature address many different problems related to such industrial enviroment, including the design, sizing, scheduling and balancing problems. The multi-product batch plant design problem is concerned to obtain the configuration of the plant and the equipment that minimize the capital cost of all the equipment items needed to fulfill the production requirements (Ravemark and Rippin, 1998). The configuration of the plant basically consists of defining how many stages, how many units at each stage, and what capacity for intermediate storages will be necessary, as well as the best factory layout.

@@

We also have the multi-product batch scheduling (MPBS) problems, in which it is necessary to determine the ideal batch size for each product and also the production sequence of the products batches based on the known demand \citep{Eilon1985}. Here, the solution must be determined in such a way that both setup and storage costs are minimized \citep{Eilon1985, Omega1993, LiuEtAl2020}. Some cientific works impose additional constraints on the MPBS problem - such as release times and due dates for each products batch production, and sequencing constraints due to mismatched product colors sequences - and focus on other goals - such as optimize customer satisfaction and/or the plant performance \citep{MendezEtAll2000, ShiEtAll2017}. Also, some cientific works consider MPBS problems within different layouts and multiperiod scenario. In parallel MPBS as well as in networked processes, it can also be necessary to define in which units each batch will be processed, and constraints that limit the units that can process each batch can also be imposed.

It is importante to note that some production units are capable of processing multiple jobs at the same time. In such a case batches of different products and sizes can be grouped and processed by these units as a single batch. It is therefore necessary to determine the set of "batches" that each new grouped batch will contain. The multi-product balancing problem consists of determining these groupings, seeking to minimize the makespan. \cite{KashanOzturk2022} name this problem \emph{p-batch} (parallel batching) in contradiction with the \emph{s-batch} (serial batching) problem where jobs are processed one by one over production facilities, as described before.

\cite{LiEtAl2022} deal with a PMPBS problem involving incompatible families with different job sizes and capacity constraints. In this problem, solutions are accepted in which two or more batches are processed simultaneously on the same machine. However, there are no production limitations for the production of each product group. The paper of \cite{LiEtAl2022} also presente an extensive literature review on production batch scheduling problems. Other important works deal with the problem of a multi-product batch plant design (MPBPD). In this case the problem is to obtain the configuration of the plant and the equipment that minimize the capital cost of all the equipment items needed to fulfill the production requirements (Ravemark and Rippin, 1998).

@@

About the solution method many papers propose mathmatical models which are solved using IBM ILOG CPLEX or another constraint programming solver.

Another not very common definition for multi-product batch production is a type of process in which several products are processed simultaneously in the same production unit.

@@

\bibitem[\protect\citeauthoryear{Kashan and Ozturk}{2022}]{KashanOzturk2022}
Kashan, A. H., and Ozturk, O. (2022). Improved MILP formulation equipped with valid inequalities for scheduling a batch processing machine with non-identical job sizes. {\it  Omega}, Vol. 112, pp. 102673.
